Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
Fix Jeff.

To allow our protocol to be utilized via Pidgin, we needed our plugin to
interface with two major aspects of the protocol: the discovery server, and the
\libmotmot library.
A libpurple protocol plugin is compiled as a statically linked library and installed into the lib directory
of Pidgin. Upon start-up Pidgin loads each of the protocol plugins in its protocol directory. If the protocol is successfully loaded, the user
can then create accounts of that specific protocol.
In order to implement a protocol, the programmer must implement a certain number of functions specifying the code to run when the user takes
an action, for example logging-in or joining a chat, in addition to listening
for input over a socket. Implemented functions are stored in a struct. Calls to libmotmot and message passing between the client and the discovery server had to be
implemented within these functions.

\subsection{Plugin Interactions with Discovery Server}
The procedure for hooking up the plugin to the discovery server is similar to the procedures in other chat protocols. Two user-info fields were
added to the account creation menu, giving the server and port of the discovery server. In the login code, a connection with the discovery server
is initiated, and once the connection is initiated an input listener is added and authentication credentials are sent. Once authentication succeeds,
status updates and friend requests are handled. We used message pack in order to have a standard message format across multiple platforms..

The input listener listens for input from the discovery server. Upon receiving a message it deserializes the message from the message pack buffer, finds
the opcode, and calls the appropriate libpurple functions based on the opcode and the rest of the data sent by the message. Writes to the discovery server
are handled in individual purple functions. Based on the user action, a message pack object is created, and the data is sent to the server across
the connection. Messages are asynchronous.

% TODO: Jeff?

>>>>

To allow our protocol to be utilized via Pidgin, we needed our plugin to
interface with two major aspects of the protocol: the discovery server, and the
\libmotmot library.  A \libpurple protocol plugin is compiled as a statically
linked library and installed into the lib directory of Pidgin. Upon start-up
Pidgin loads each of the protocol plugins in its protocol directory. If the
protocol is successfully loaded, the user can then create accounts of that
specific protocol.  In order to implement a protocol, the programmer must
implement a certain number of functions specifying the code to run when the user
takes an action, for example logging-in or joining a chat, in addition to
listening for input over a socket. Implemented functions are stored in a struct.
Calls to \libmotmot and message passing between the client and the discovery
server had to be implemented within these functions.

\subsection{Plugin Interactions with Discovery Server}
The procedure for hooking up the plugin to the discovery server is similar to
the procedures in other chat protocols. Two user-info fields were added to the
account creation menu, giving the server and port of the discovery server. In
the login code, a connection with the discovery server is initiated, and once
the connection is initiated an input listener is added and authentication
credentials are sent. Once authentication succeeds, status updates and friend
requests are handled. We used message pack in order to have a standard message
format across multiple platforms.

The input listener listens for input from the discovery server. Upon receiving a
message it deserializes the message from the message pack buffer, finds the
opcode, and calls the appropriate \libpurple functions based on the opcode and
the rest of the data sent by the message. Writes to the discovery server are
handled in individual purple functions. Based on the user action, a message pack
object is created, and the data is sent to the server across the connection.
Messages are asynchronous.
